Data cleaning for Project

### 2025-03-12 code/processing-code/processingfile-v1.qmd
project part 3

```{r}
#loading the necessary packages
library(here)
library(dplyr)
library(skimr)
library(ggplot2)
library(readxl)
library(tidyr)
```

@@

>>>>

```{r}
#loading the necessary packages
library(here)
library(dplyr)
library(skimr)
library(ggplot2)
library(readxl)
library(tidyr)
library(writexl)
```

@@

Saving an excel file as well.

```{r}
xl_path <- here("data", "processed-data", "processeddata.xlsx")
writexl::write_xlsx(processeddata, xl_path)
```
